Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-01-22 R0V0.tex
Changes in the ADMM paragraph

\mypara Note that the ADMM cannot be used to solve the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual}. The reason is the fact that $B_\perp\equiv0$.

@@

>>>>

\mypara Solving the matrix inequality~\eqref{eq:Artstein-Sontag:inequality:dual} with ADMM, the components of the matrix $W$ obtained are shown in Equation~??

@@

\begin{table}
	\begin{tabular}{r|l}
	Method&Time taken by the solver [s]\\ \hline
	Chordal graph decomposition&2.6 to 98\\
	ADMM&
	\end{tabular}
\end{table}
